Models

### 2022-09-19 analysis/05_model_metrics.Rmd

Fit models
```{r}
#Fit models with base settings
mod_results <- pmap_dfr(mods, get_model, data = model_data)

@@

#this is a list of models that weren't fit because there weren't enough timeseries OR they didn't converge
#min_litter_size just won't converge
missing_mods <- setdiff(uniq_mods, uniq_metric_model)
```

>>>>

Fit models
```{r}
#exclude amphibians
model_data <- model_data %>% filter(taxa != "Amphibians")

#Fit models with base settings
mod_results <- pmap_dfr(mods, get_model, data = model_data)

@@

#this is a list of models that weren't fit because there weren't enough timeseries OR they didn't converge
#most are amphibian traits or traits only found for one taxa (with taxa as a covariate), the nectar diet realm model wouldn't converge
missing_mods <- setdiff(uniq_mods, uniq_metric_model)
```
